\ourlongtitle

### 2021-08-23 Bernoulli/glo-2020.tex
Added revised version

\usepackage[linesnumbered,vlined]{algorithm2e}
\usepackage{bbm}
\usepackage{color}
\usepackage{enumitem}
%\usepackage{graphicx}
\usepackage{ifthen}
\usepackage{mathtools}  
%\usepackage{mnsymbol}
\usepackage{stmaryrd}
\usepackage{tikz}
\usetikzlibrary{fit,positioning}
\usepackage{xargs}

@@

\include{glo-2020-def}

@@

\begin{frontmatter}
\title{Supplement to `Pseudo-marginal PaRIS samplers'}
%\title{A sample article title with some additional note\thanksref{t1}}
\runtitle{Supplement to `Pseudo-marginal PaRIS samplers'}
%\thankstext{t1}{Working title.}

\begin{aug}
\author[A]{\fnms{Pierre} \snm{Gloaguen}\ead[label=e1]{pierre.gloaguem@agroparistech.fr}},
\author[B]{\fnms{Sylvain} \snm{Le Corff}\ead[label=e2]{sylvain-lecorff@telecom-sudparis.eu}}
\and
\author[C]{\fnms{Jimmy} \snm{Olsson}\ead[label=e3]{jimmyol@kth.se}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Addresses                                %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\address[A]{Department,
AgroParisTech, Paris, France.
\printead{e1}}

\address[B]{Department,
T\'el\'ecom SudParis, Paris, France.
\printead{e2}}

\address[C]{Department,
KTH Royal Institute of Technology, Stockholm, Sweden. 
\printead{e3}}

@@

\begin{abstract}
Here we will put a concise abstract.
\end{abstract}

\begin{keyword}
\kwd{First keyword}
\kwd{second keyword}
\end{keyword}

@@

\section{Application to tangent filter approximation}
\label{sec:tangent:filter}
\noteJO{We need to find an alternative term for `tangent filter' in the Feynman-Kac setting. Check the paper by Del Moral.}

\section{Numerical results}
\label{sec:numerical:results}

%\appendix

\section{Proofs}
\label{sec:proofs}
\input{glo-2020-proofs}

\section{Technical results}
\label{sec:tech:results}
\input{glo-2020-tech-results}

@@

@@

This template helps you to create a properly formatted \LaTeXe\ manuscript.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% `\ ' is used here because TeX ignores    %%
%% spaces after text commands.              %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Prepare your paper in the same style as used in this sample .pdf file.
Try to avoid excessive use of italics and bold face.
Please do not use any \LaTeXe\ or \TeX\ commands that affect the layout
or formatting of your document (i.e., commands like \verb|\textheight|,
\verb|\textwidth|, etc.).

\section{Section headings}
Here are some sub-sections:
\subsection{A sub-section}
Regular text.
\subsubsection{A sub-sub-section}
Regular text.

\section{Text}
\subsection{Lists}

The following is an example of an \emph{itemized} list,
two levels deep.
\begin{itemize}
\item
This is the first item of an itemized list.  Each item
in the list is marked with a ``tick.''  The document
style determines what kind of tick mark is used.
\item
This is the second item of the list.  It contains another
list nested inside it.
\begin{itemize}
\item This is the first item of an itemized list that
is nested within the itemized list.
\item This is the second item of the inner list.  \LaTeX\
allows you to nest lists deeper than you really should.
\end{itemize}
This is the rest of the second item of the outer list.
\item
This is the third item of the list.
\end{itemize}

The following is an example of an \emph{enumerated} list of one level.

\begin{enumerate}
\item This is the first item of an enumerated list.
\item This is the second item of an enumerated list.
\end{enumerate}

The following is an example of an \emph{enumerated} list, two levels deep.
\begin{enumerate}
\item[1.]
This is the first item of an enumerated list.  Each item
in the list is marked with a ``tick.''  The document
style determines what kind of tick mark is used.
\item[2.]
This is the second item of the list.  It contains another
list nested inside of it.
\begin{enumerate}
\item
This is the first item of an enumerated list that
is nested within.
\item
This is the second item of the inner list.  \LaTeX\
allows you to nest lists deeper than you really should.
\end{enumerate}
This is the rest of the second item of the outer list.
\item[3.]
This is the third item of the list.
\end{enumerate}

\subsection{Punctuation}
Dashes come in three sizes: a hyphen, an intra-word dash like ``$U$-statistics'' or ``the time-homogeneous model'';
a medium dash (also called an ``en-dash'') for number ranges or between two equal entities like ``1--2'' or ``Cauchy--Schwarz inequality'';
and a punctuation dash (also called an ``em-dash'') in place of a comma, semicolon,
colon or parentheses---like this.

Generating an ellipsis \ldots\ with the right spacing
around the periods requires a special command.

\section{Fonts}
Please use text fonts in text mode, e.g.:
\begin{itemize}
\item[]\textrm{Roman}
\item[]\textit{Italic}
\item[]\textbf{Bold}
\item[]\textsc{Small Caps}
\item[]\textsf{Sans serif}
\item[]\texttt{Typewriter}
\end{itemize}
Please use mathematical fonts in mathematical mode, e.g.:
\begin{itemize}
\item[] $\mathrm{ABCabc123}$
\item[] $\mathit{ABCabc123}$
\item[] $\mathbf{ABCabc123}$
\item[] $\boldsymbol{ABCabc123\alpha\beta\gamma}$
\item[] $\mathcal{ABC}$
\item[] $\mathbb{ABC}$
\item[] $\mathsf{ABCabc123}$
\item[] $\mathtt{ABCabc123}$
\item[] $\mathfrak{ABCabc123}$
\end{itemize}
Note that \verb|\mathcal, \mathbb| belongs to capital letters-only font typefaces.

\section{Notes}
Footnotes\footnote{This is an example of a footnote.}
pose no problem.\footnote{Note that footnote number is after punctuation.}

\section{Quotations}

Text is displayed by indenting it from the left margin. There are short quotations
\begin{quote}
This is a short quotation.  It consists of a
single paragraph of text.  There is no paragraph
indentation.
\end{quote}
and longer ones.
\begin{quotation}
This is a longer quotation.  It consists of two paragraphs
of text.  The beginning of each paragraph is indicated
by an extra indentation.

This is the second paragraph of the quotation.  It is just
as dull as the first paragraph.
\end{quotation}

\section{Environments}

\subsection{Examples for \emph{\texttt{plain}}-style environments}
\begin{axiom}\label{ax1}
This is the body of Axiom \ref{ax1}.
\end{axiom}

\begin{proof}
This is the body of the proof of the axiom above.
\end{proof}

\begin{claim}\label{cl1}
This is the body of Claim \ref{cl1}. Claim \ref{cl1} is numbered after
Axiom \ref{ax1} because we used \verb|[axiom]| in \verb|\newtheorem|.
\end{claim}

\begin{theorem}\label{th1}
This is the body of Theorem \ref{th1}. Theorem \ref{th1} numbering is
dependent on section because we used \verb|[section]| after \verb|\newtheorem|.
\end{theorem}

\begin{theorem}[Title of the theorem]\label{th2}
This is the body of Theorem \ref{th2}. Theorem \ref{th2} has additional title.
\end{theorem}

\begin{lemma}\label{le1}
This is the body of Lemma \ref{le1}. Lemma \ref{le1} is numbered after
Theorem \ref{th2} because we used \verb|[theorem]| in \verb|\newtheorem|.
\end{lemma}

\begin{proof}[Proof of Lemma \ref{le1}]
This is the body of the proof of Lemma \ref{le1}.
\end{proof}

\subsection{Examples for \emph{\texttt{remark}}-style environments}
\begin{definition}\label{de1}
This is the body of Definition \ref{de1}. Definition \ref{de1} is numbered after
Lemma \ref{le1} because we used \verb|[theorem]| in \verb|\newtheorem|.
\end{definition}

\begin{example}
This is the body of the example. Example is unnumbered because we used \verb|\newtheorem*|
instead of \verb|\newtheorem|.
\end{example}

\begin{fact}
This is the body of the fact. Fact is unnumbered because we used \verb|\newtheorem*|
instead of \verb|\newtheorem|.
\end{fact}

\section{Tables and figures}
Cross-references to labeled tables: As you can see in Table~\ref{sphericcase}
and also in Table~\ref{parset}.

\begin{table*}
\caption{The spherical case ($I_1=0$, $I_2=0$)}
\label{sphericcase}
\begin{tabular}{@{}lrrrrc@{}}
\hline
Equil. \\
points & \multicolumn{1}{c}{$x$}
& \multicolumn{1}{c}{$y$} & \multicolumn{1}{c}{$z$}
& \multicolumn{1}{c}{$C$} & S \\
\hline
$L_1$    & $-$2.485252241 & 0.000000000  & 0.017100631  & 8.230711648  & U \\
$L_2$    & 0.000000000  & 0.000000000  & 3.068883732  & 0.000000000  & S \\
$L_3$    & 0.009869059  & 0.000000000  & 4.756386544  & $-$0.000057922 & U \\
$L_4$    & 0.210589855  & 0.000000000  & $-$0.007021459 & 9.440510897  & U \\
$L_5$    & 0.455926604  & 0.000000000  & $-$0.212446624 & 7.586126667  & U \\
$L_6$    & 0.667031314  & 0.000000000  & 0.529879957  & 3.497660052  & U \\
$L_7$    & 2.164386674  & 0.000000000  & $-$0.169308438 & 6.866562449  & U \\
$L_8$    & 0.560414471  & 0.421735658  & $-$0.093667445 & 9.241525367  & U \\
$L_9$    & 0.560414471  & $-$0.421735658 & $-$0.093667445 & 9.241525367  & U \\
$L_{10}$ & 1.472523232  & 1.393484549  & $-$0.083801333 & 6.733436505  & U \\
$L_{11}$ & 1.472523232  & $-$1.393484549 & $-$0.083801333 & 6.733436505  & U \\
\hline
\end{tabular}
\end{table*}

\begin{table}
\caption{Sample posterior estimates for each model}
\label{parset}
%
\begin{tabular}{@{}lcrcrrr@{}}
\hline
&& & &\multicolumn{3}{c}{Quantile} \\
\cline{5-7}
Model &Parameter &
\multicolumn{1}{c}{Mean} &
Std. dev.&
\multicolumn{1}{c}{2.5\%} &
\multicolumn{1}{c}{50\%}&
\multicolumn{1}{c@{}}{97.5\%} \\
\hline
{Model 0} & $\beta_0$ & $-$12.29 & 2.29 & $-$18.04 & $-$11.99 & $-$8.56 \\
          & $\beta_1$  & 0.10   & 0.07 & $-$0.05  & 0.10   & 0.26  \\
          & $\beta_2$   & 0.01   & 0.09 & $-$0.22  & 0.02   & 0.16  \\[6pt]
{Model 1} & $\beta_0$   & $-$4.58  & 3.04 & $-$11.00 & $-$4.44  & 1.06  \\
          & $\beta_1$   & 0.79   & 0.21 & 0.38   & 0.78   & 1.20  \\
          & $\beta_2$   & $-$0.28  & 0.10 & $-$0.48  & $-$0.28  & $-$0.07 \\[6pt]
{Model 2} & $\beta_0$   & $-$11.85 & 2.24 & $-$17.34 & $-$11.60 & $-$7.85 \\
          & $\beta_1$   & 0.73   & 0.21 & 0.32   & 0.73   & 1.16  \\
          & $\beta_2$   & $-$0.60  & 0.14 & $-$0.88  & $-$0.60  & $-$0.34 \\
          & $\beta_3$   & 0.22   & 0.17 & $-$0.10  & 0.22   & 0.55  \\
\hline
\end{tabular}
%
\end{table}

\begin{figure}
\includegraphics{figure1}
\caption{Pathway of the penicillin G biosynthesis.}
\label{penG}
\end{figure}

Sample of cross-reference to figure.
Figure~\ref{penG} shows that it is not easy to get something on paper.

\section{Equations and the like}

Two equations:
\begin{equation}
    C_{s}  =  K_{M} \frac{\mu/\mu_{x}}{1-\mu/\mu_{x}} \label{ccs}
\end{equation}
and
\begin{equation}
    G = \frac{P_{\mathrm{opt}} - P_{\mathrm{ref}}}{P_{\mathrm{ref}}}  100(\%).
\end{equation}

Equation arrays:
\begin{eqnarray}
  \frac{dS}{dt} & = & - \sigma X + s_{F} F,\\
  \frac{dX}{dt} & = &   \mu    X,\\
  \frac{dP}{dt} & = &   \pi    X - k_{h} P,\\
  \frac{dV}{dt} & = &   F.
\end{eqnarray}
One long equation:
\begin{eqnarray}
 \mu_{\text{normal}} & = & \mu_{x} \frac{C_{s}}{K_{x}C_{x}+C_{s}}  \nonumber\\
                     & = & \mu_{\text{normal}} - Y_{x/s}\bigl(1-H(C_{s})\bigr)(m_{s}+\pi /Y_{p/s})\nonumber\\
                     & = & \mu_{\text{normal}}/Y_{x/s}+ H(C_{s}) (m_{s}+ \pi /Y_{p/s}).
\end{eqnarray}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Example with single Appendix:            %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{appendix}
\section*{Title}\label{appn} %% if no title is needed, leave empty \section*{}.
Appendices should be provided in \verb|{appendix}| environment,
before Acknowledgements.

If there is only one appendix,
then please refer to it in text as \ldots\ in the \hyperref[appn]{Appendix}.
\end{appendix}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Example with multiple Appendixes:        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{appendix}
\section{Title of the first appendix}\label{appA}
If there are more than one appendix, then please refer to it
as \ldots\ in Appendix \ref{appA}, Appendix \ref{appB}, etc.

\section{Title of the second appendix}\label{appB}
\subsection{First subsection of Appendix \protect\ref{appB}}

Use the standard \LaTeX\ commands for headings in \verb|{appendix}|.
Headings and other objects will be numbered automatically.
\begin{equation}
\mathcal{P}=(j_{k,1},j_{k,2},\dots,j_{k,m(k)}). \label{path}
\end{equation}

Sample of cross-reference to the formula (\ref{path}) in Appendix \ref{appB}.
\end{appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Support information (funding), if any,   %%
%% should be provided in the                %%
%% Acknowledgements section.                %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
The authors would like to thank the anonymous referees, an Associate
Editor and the Editor for their constructive comments that improved the
quality of this paper.

The first author was supported by NSF Grant DMS-??-??????.

The second author was supported in part by NIH Grant ???????????.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Supplementary Material, if any, should   %%
%% be provided in {supplement} environment  %%
%% with title and short description.        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{supplement}
\stitle{Title of Supplement A}
\sdescription{Short description of Supplement A.}
\end{supplement}
\begin{supplement}
\stitle{Title of Supplement B}
\sdescription{Short description of Supplement B.}
\end{supplement}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                  The Bibliography                       %%
%%                                                         %%
%%  imsart-number.bst  will be used to                     %%
%%  create a .BBL file for submission.                     %%
%%                                                         %%
%%  Note that the displayed Bibliography will not          %%
%%  necessarily be rendered by Latex exactly as specified  %%
%%  in the online Instructions for Authors.                %%
%%                                                         %%
%%  MR numbers will be added by VTeX.                      %%
%%                                                         %%
%%  Use \cite{...} to cite references in text.             %%
%%                                                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% if your bibliography is in bibtex format, uncomment commands:
%\bibliographystyle{imsart-number} % Style BST file
%\bibliography{bibliography}       % Bibliography file (usually '*.bib')

%% or include bibliography directly:
%\begin{thebibliography}{4}
\bibliographystyle{plain}
\bibliography{glo-2020}

%\bibitem{r1}
%Billingsley, P. (1999). \textit{Convergence of
%Probability Measures}, 2nd ed.
%New York: Wiley.
%
%\bibitem{r2}
%Bourbaki, N.  (1966). \textit{General Topology}  \textbf{1}.
%Reading, MA: Addison--Wesley.
%
%\bibitem{r3}
%Ethier, S. N. and Kurtz, T. G. (1985).
%\textit{Markov Processes: Characterization and Convergence}.
%New York: Wiley.
%
%\bibitem{r4}
%Prokhorov, Yu. (1956).
%Convergence of random processes and limit theorems in probability
%theory. \textit{Theory  Probab.  Appl.}
%\textbf{1} 157--214.

%\end{thebibliography}

>>>>

\usepackage[linesnumbered,vlined]{algorithm2e}
\usepackage{bbm}
\usepackage{caption}
\usepackage{color}
\usepackage{enumitem}
%\usepackage{graphicx}
\usepackage{ifthen}
\usepackage{mathtools}  
%\usepackage{mnsymbol}
\usepackage{stmaryrd}
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{fit,positioning}
\usepackage{xargs}

@@

\include{glo-2020-def}
\newcommand{\ourlongtitle}{A pseudo-marginal sequential Monte Carlo online smoothing algorithm}
\newcommand{\ourshorttitle}{A pseudo-marginal SMC online smoothing algorithm}

@@

\begin{frontmatter}
\title{\ourlongtitle} %PaRIS samplers}
%\title{A sample article title with some additional note\thanksref{t1}}
\runtitle{\ourshorttitle} %PaRIS samplers}
%\thankstext{t1}{Working title.}

\begin{aug}
\author[A]{\fnms{Pierre} \snm{Gloaguen}\ead[label=e1]{pierre.gloaguem@agroparistech.fr}},
\author[B]{\fnms{Sylvain} \snm{Le Corff}\ead[label=e2]{sylvain-lecorff@telecom-sudparis.eu}}
\and
\author[C]{\fnms{Jimmy} \snm{Olsson}\ead[label=e3]{jimmyol@kth.se}}
%%%%%%%%%%
%% Addresses                            
%%%%%%%%%%
\address[A]{AgroParisTech, Paris, France.
\printead{e1}}

\address[B]{T\'el\'ecom SudParis, Paris, France.
\printead{e2}}

\address[C]{KTH Royal Institute of Technology, Stockholm, Sweden. 
\printead{e3}}

@@

\begin{abstract}
We consider online computation of expectations of additive state functionals under general path probability measures proportional to products of unnormalised transition densities. These transition densities are assumed to be intractable but possible to estimate, with or without bias. Using pseudo-marginalisation techniques we are able to extend the particle-based, rapid incremental smoother (PaRIS) algorithm proposed in [J.~Olsson and J.~Westerborn. Efficient particle-based online smoothing in general hidden Markov models: The {PaRIS} algorithm. {\em Bernoulli}, 23(3):1951--1996, 2017] to this setting. The resulting algorithm, which has a linear complexity in the number of particles and constant memory requirements, applies to a wide range of challenging path-space Monte Carlo problems, including smoothing in partially observed diffusion processes and models with intractable likelihood. The algorithm is furnished with several theoretical results, including a central limit theorem, establishing its convergence and numerical stability. Moreover, under strong mixing assumptions we establish a novel $\mathcal{O}(n \precpar)$ bound on the asymptotic bias of the algorithm, where $n$ is the path length and $\precpar$ controls the bias of the density estimators. 
\end{abstract}

\begin{keyword}
\kwd{central limit theorem}
\kwd{exponential concentration}
\kwd{partially observed diffusions}
\kwd{particle smoothing}
\kwd{pseudo-marginal methods}
\kwd{sequential Monte Carlo methods}
\end{keyword}

@@

\section{A numerical example}
\label{sec:numerical:results}
\input{glo-2020-numerics}

%\begin{appendix}

%\section{Proofs}
%\label{sec:proofs}
%\input{glo-2020-proofs}

%\end{appendix}

@@

%%%%%%%%%%%%%%
%% Supplementary paper 
%%%%%%%%%%%%%%

\begin{frontmatter}
\title{Supplement to `\ourlongtitle'}
\runtitle{Supplement to `\ourshorttitle'}

\begin{aug}
\author[A]{\fnms{Pierre} \snm{Gloaguen}\ead[label=e1]{pierre.gloaguem@agroparistech.fr}},
\author[B]{\fnms{Sylvain} \snm{Le Corff}\ead[label=e2]{sylvain-lecorff@telecom-sudparis.eu}}
\and
\author[C]{\fnms{Jimmy} \snm{Olsson}\ead[label=e3]{jimmyol@kth.se}}
%%%%%%%%%%
%% Addresses                                
%%%%%%%%%%
\address[A]{AgroParisTech, Paris, France.
\printead{e1}}

\address[B]{T\'el\'ecom SudParis, Paris, France.
\printead{e2}}

\address[C]{KTH Royal Institute of Technology, Stockholm, Sweden. 
\printead{e3}}

\begin{abstract}
We provide the proofs of, in order, Lemma~\ref{lem:reversibility}, Theorem~\ref{cor:hoeffding:tau:marginal}, Theorem~\ref{cor:clt:pseudo:marginal:paris}, Theorem~\ref{thm:bias:bound}, Theorem~\ref{thm:variance:bound}, Corollary~\ref{cor:variance:bound}, and Proposition~\ref{prop:variance:bound:filter} in  [P.~Gloaguen, S.~Le Corff and J.~Olsson. \ourlongtitle. Submitted.]. 
\end{abstract}

\begin{keyword}
\kwd{Central limit theorem}
\kwd{exponential concentration}
\kwd{partially observed diffusions}
\kwd{particle smoothing}
\kwd{pseudo-marginal methods}
\kwd{sequential Monte Carlo methods}
\end{keyword}

%%% Proof of backward decomposition

\input{glo-2020-proof-bwd-decomp}

%%% Proof of particle asymptotics

\input{glo-2020-proof-asymp}

%%% Proof of bias bounds

\section{Proof of Theorem~\ref{thm:bias:bound}}
\label{sec:proofs}
\input{glo-2020-proofs}

\section{Proofs of Theorem~\ref{thm:variance:bound}, Corollary~\ref{cor:variance:bound}, and Proposition~\ref{prop:variance:bound:filter}}
\label{sec:variance:bounds}
\input{glo-2020-proof-stability}

\section{A technical lemma}
\label{sec:tech:results}
\input{glo-2020-tech-results}

@@
